RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-10-11 main.tex
:construction: Add notes
:paintbrush: Add scattering comparison

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage[american]{circuitikz}
\usepackage{cite}
\usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage[subtle]{savetrees}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tikz}
\usepackage{xcolor}

@@

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communications}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}

@@

		The backscatter reader can be either co-located or separated with the carrier emitter, known as monostatic and bistatic \gls{bc} in Fig. \subref*{fi:monostatic_backscatter_communication} and \subref*{fi:bistatic_backscatter_communication}, respectively.

@@

		\begin{figure}[!t]
			\centering
			\subfloat[Monostatic \gls{bc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/monostatic_backscatter_communication.tex}
				}
				\label{fi:monostatic_backscatter_communication}
			}
			\subfloat[Bistatic \gls{bc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/bistatic_backscatter_communication.tex}
				}
				\label{fi:bistatic_backscatter_communication}
			}
			\\
			\subfloat[\gls{ambc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/ambient_backscatter_communication.tex}
				}
				\label{fi:ambient_backscatter_communication}
			}
			\subfloat[\gls{sr}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/symbiotic_radio.tex}
				}
				\label{fi:symbiotic_radio}
			}
			\\
			\subfloat[\gls{ris}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/reconfigurable_intelligent_surface.tex}
				}
				\label{fi:reconfigurable_intelligent_surface}
			}
			\subfloat[RIScatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/riscatter.tex}
				}
				\label{fi:riscatter}
			}
			\caption{
				Paradigms for various scattering applications.
			}
			\label{fi:scatter_comparison}
		\end{figure}
	\end{subsection}

@@

@@

		\emph{First,} we propose RIScatter nodes to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
		The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation with passive beamforming.
		Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
		Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) RIScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional equiprobable line coding in \gls{bc}/\gls{sr}; 4) the potentially dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.

>>>>

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage{booktabs}
\usepackage[american]{circuitikz}
\usepackage{cite}
\usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage[subtle]{savetrees}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{xcolor}

@@

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communications}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{mbc}{MBC}{Monostatic Backscatter Communications}
\newacronym{bbc}{BBC}{Bistatic Backscatter Communications}

@@

		The backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig. \subref*{fi:monostatic_backscatter_communication} and \subref*{fi:bistatic_backscatter_communication}, respectively.

@@

		\begin{figure}[!t]
			\centering
			\subfloat[\gls{mbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/monostatic_backscatter_communication.tex}
				}
				\label{fi:monostatic_backscatter_communication}
			}
			\subfloat[\gls{bbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/bistatic_backscatter_communication.tex}
				}
				\label{fi:bistatic_backscatter_communication}
			}
			\\
			\subfloat[\gls{ambc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/ambient_backscatter_communication.tex}
				}
				\label{fi:ambient_backscatter_communication}
			}
			\subfloat[\gls{sr}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/symbiotic_radio.tex}
				}
				\label{fi:symbiotic_radio}
			}
			\\
			\subfloat[\gls{ris}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/reconfigurable_intelligent_surface.tex}
				}
				\label{fi:reconfigurable_intelligent_surface}
			}
			\subfloat[RIScatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/riscatter.tex}
				}
				\label{fi:riscatter}
			}
			\caption{
				Illustration of scattering applications.
				% Paradigms for various scattering applications.
			}
			\label{fi:scatter_comparison}
		\end{figure}
	\end{subsection}

	\begin{table*}[]
		\caption{Comparison of Scattering Applications}
		\begin{tabularx}{\textwidth}{XXXXXXX}
			\toprule
			                              & \gls{mbc}               & \gls{bbc}               & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                       & RIScatter                                         \\ \midrule
			Coexisting systems            & 1                       & 1                       & 2 (competitive)                                 & 2 (collaborative)                            & 1                               & 2 (collaborative)                                 \\ \midrule
			Scatterer contribution        & Backscatter modulation  & Backscatter modulation  & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming             & Backscatter modulation and passive beamforming    \\ \midrule
			Cooperative transmission      & ---                     & ---                     & No                                              & Active beamforming                           & ---                             & Active beamforming and smart reflection           \\ \midrule
			Cooperative reception         & ---                     & ---                     & No                                              & Joint detection or \gls{sic}                 & ---                             & Backscatter detection as primary channel training \\ \midrule
			Backscatter detection         & Coherent or noncoherent & Coherent or noncoherent & Semi-coherent or noncoherent                    & Coherent                                     & ---                             & Semi-coherent                                     \\ \midrule
			Reflection state distribution & Equiprobable            & Equiprobable            & Equiprobable                                    & Gaussian or Equiprobable                     & Degenerate (\gls{csi}-adaptive) & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
			Load-switching frequency      & Fast or slow            & Fast or slow            & Fast or slow                                    & Slow                                         & Slow (dynamic) or very slow     & Fast or slow                                      \\ \bottomrule
		\end{tabularx}
	\end{table*}

@@

	% TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
	% TODO cooperative input design can be used for co-located RIScatter nodes.
	% TODO hardward to modulate using RIS is already available.
	% TODO RIScatter: enhance backscatter signal difference (suppress primary interference) or primary signal strength.
	% TODO For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
	% TODO RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
	% TODO Redefine RIS using book
	% TODO Using RIS to encode is not very interesting as controller is anyway usable
	% TODO Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communications], fast load switching speed is key for high data rate - symbol ratio is not very large
	% TODO Beamforming can cancel direct interference to avoid the collapse of non-coherent energy detection and enlarge energy gap.
	% ? [Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communications Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
	% TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
	% TODO convergence
	% TODO channel coding: general non-adaptive (book) adaptive (DMC)
	% ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
	% TODO mu-code: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
	% TODO backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
	% TODO semicoherent: known CSI, unknown primary/backscatter symbols

@@

		\emph{First,} we propose RIScatter nodes to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
		The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation with passive beamforming.
		Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
		Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with ambient devices, but the advantages are
		1) RIScatter nodes can be built over universal load-switching scatterers instead of composite metamaterial;
		2) backscatter modulation and passive beamforming are unified by adaptive input distribution instead of advanced hardware architecture;
		3) optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients;
		4) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional equiprobable line coding in \gls{bc}/\gls{sr};
		5) the potentially dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.
